tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-09-15 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
berg: stats comparison mero-asex-malegam heatmap and save proportional bar chart
Fix stacked_barchart_fun standev error bars and stat comp heatmaps

```{r stacked_barchart}
sd_bars <- TRUE
g_list <- stacked_barchart(melted_tpm,
                           stack_group_name = 'SorL',
                           sd_bars = sd_bars,
                           inset = TRUE)

@@

  grid.newpage()
  grid.draw(g)
```

>>>>

```{r stacked_barchart}
sd_bars <- TRUE
g_list <- stacked_barchart(melted_tpm = melted_tpm,
                           stack_group_name = 'SorL',
                           sd_bars = sd_bars,
                           inset = TRUE)

@@

grid.newpage()
grid.draw(g)

ggsave('plots/thesis_chapter3_figure_propBarChart_subFam.png',
       width = 7,
       height = 5,
       units = "in",
       g)
```

### 2021-09-15 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Fix stacked_barchart_fun standev error bars and stat comp heatmaps

```{r running_qusage_malevfemale}
maleVfemale <- lapply(
  list(pir_geneset), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Gam.Male-Gam.Female',
                                gene_list,
                                n.points = 2^18)

lapply(maleVfemale, getElement, 'qstable')
```

@@

```{r}
max_logfold <- ceiling(max(max(berghei_comparison_stats_df$log.fold.change), 
                           abs(min(berghei_comparison_stats_df$log.fold.change))))

(
  x <- ggplot(filter(berghei_comparison_stats_df,
                     FDR < 0.05), 
              aes(x = contrast, 
                  y = reorder(pathway.name, dplyr::desc(pathway.name)))) +
    xlab('Comparison') + ylab('Geneset') + 
    # scale_x_discrete(labels= c(1,2,3,4,6)) +
    geom_count(aes(
      colour = log.fold.change), 
      na.rm = TRUE) +
    labs(colour = 'log2 Fold Change') +
    scale_color_gradientn(
      colours = rev(brewer.pal(11, "RdBu")),
      na.value="transparent",
      limits = c(-max_logfold,max_logfold),
      # limits = c(-0.5,1.25)
    ) +
    scale_size_area(max_size = 6) +
    theme_bw() +
    theme(panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = 'white'),
          plot.background = element_blank(),
          legend.background = element_rect(fill = 'transparent'),
          axis.text.x = element_text(angle = 90))
)
```

@@

order_path.names <- ordering(unique(mero_asex_malegam_stats_df$pathway.name), 
                             order_vector = c('pir', 
                                              'L', 'L[[:digit:]]', 
                                              'S', 'S[[:digit:]]'))

@@

>>>>

@@

@@

order_path.names <- ordering(sort(unique(mero_asex_malegam_stats_df$pathway.name)), 
                             order_vector = c('pir', 
                                              'L', 'L[[:digit:]]', 
                                              'S', 'S[[:digit:]]'))

@@

```{r running_qusage_stage_by_stage}
ordered_stages <- ordering(unique(lifeCycle_labels),
         order_vector = r_order_vector)

comparisons <- c(
  unlist(
    lapply(seq_along(ordered_stages),
           function(i){ if(i < length(ordered_stages)){ paste0(ordered_stages[i],'-',ordered_stages[i+1]) } }
    )
  ),
  'Asex.Schiz-Gam.Male',
  'Ook-Sporoz'
)

#Remove some comparisons
comparisons <- comparisons[!grepl(comparisons, pattern = 'Asex\\.Mixed-Asex\\.Ring')]

all_comparisons <- lapply(comparisons, 
                          function(comparison){
                            list_comp <- lapply(
                              list(pir_geneset,
                                   ShortLong_list,
                                   subfam_list), 
                              function(gene_list){
                                qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                                            lifeCycle_labels,
                                                            comparison,
                                                            gene_list,
                                                            n.points = 2^18)
                                list(results = qs.results.subfam, 
                                     qstable = qsTable(qs.results.subfam) %>% 
                                       mutate(contrast = qs.results.subfam$contrast))
                              })
                            names(list_comp) <- c('pir', 'shortlong', 'subfam')
                            list_comp$combined <- bind_rows(lapply(list_comp, 
                                                                   getElement, 
                                                                   'qstable'))
                            return(list_comp)
                          })
names(all_comparisons) <- comparisons

all_stats_df <- lapply(all_comparisons, getElement, 'combined') %>% 
  bind_rows %>% 
  mutate(fdr_r = p.adjust(p.Value, method = 'fdr')) %>% 
  arrange(fdr_r)

all_stats_df <- all_stats_df[order(match(all_stats_df$pathway.name,order_path.names)),]

all_stats_df_cast <- dcast(all_stats_df,
                           contrast ~ pathway.name,
                           value.var = 'log.fold.change') %>% 
  column_to_rownames(var = 'contrast')

all_stats_df_cast <- all_stats_df_cast[ordering(rownames(all_stats_df_cast),
                                                r_order_vector),
                                       order_path.names]

Heatmap(all_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          fdr_val <- all_stats_df[
            all_stats_df$contrast == rownames(all_stats_df_cast[i,]),
          ]$fdr_r[j]
          if(fdr_val<= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold')
            )
          }
        })
```
